\large{\bf Large effects and the infinitesimal model }

### 2024-02-21 review-responses.tex

\vskip 4em

\pagebreak

%%%%%%%%%%%%%%
\section*{AE comments:}

\begin{quote}
It would be good to try to address the remaining concern of Reviewer 1 and to
clarify the corresponding assumption on which your analysis seems to rest.
After that, the paper will be accepted for publication without further
reviewing.  
\end{quote}

Thanks very much, and apologies such a minor change took some time.
We've tried our best here.

@@

%%%%%%%%%%%%%%
\reviewersection{1}

\begin{point}{}
I don't think the authors quite address the point I had raised, and their
response and also the change in the paper that they make \revref{} is
rather cryptic and hard to understand. I think all that I was trying to say was
that the independence of allelic states, i.e., the LE assumption, is a big part
of their argument but not of the original infinitesimal model or of the TPB
2017 paper. And I thus felt that it is important to highlight the rather
limited nature of their proposition, which I don't think quite comes across.
\end{point}

\paragraph{Reply:}
Although what you're saying here seems very clear,
we must be talking past each other somehow,
since \citet{barton2017infinitesimal} unambiguously \emph{does} assume LE,
for at least the main results on
``the infinitesimal model as the limit of Mendelian inheritance''.
In \citet{barton2017infinitesimal}, Assumption (4) (``Ancestral population'')
on page 58 of the TPB PDF,
a prerequisite to the main convergence results, says:
``\emph{Although it is not strictly necessary,
we assume that in generation zero, the individuals that
found the pedigree are unrelated. They are sampled from
an ancestral population in which all loci are assumed to be
in linkage equilibrium.}''

Of course, loci in \emph{subsequent} generations won't be in LE,
and we assumed in our previous revision that this is what the reviewer was referring to.
Our argument here is that if the infinitesimal model
is not a good model for this simplest LE situation,
then it won't be in subsequent generations also.

Perhaps by ``the original infinitesimal model or the TPB 2017 paper'',
the reviewer means something different than these convergence results?
We certainly agree that \emph{the infinitesimal model},
stated as a phenomenological model for trait inheritance,
does not make any assumptions whatsoever about the precise genetic basis
(including linkage equilibrium or not).
However, that's probably not what the reviewer means, since that's entirely
beside the point (as in this section of the paper we're looking at
consequences of the genetic basis)?

In summary, we're probably missing something,
but despite significant thinking, haven't figured out what it might be.
We've tried (again) to clarify the general point;
maybe it will help.

### 2024-02-21 writeup.tex
final response to reviewers

Since the Mendelian sampling term is a sum of terms of the form
$$
    (X_\ell - 1/2) \eta_\ell^{[1]} + (1/2 - X_\ell) \eta_\ell^{[2]},
$$
the appropriate central limit theorem for the sum is determined by
the tail behavior of $|(X - 1/2) \eta|$,  \revpoint{2}{1}
where $X$ is Bernoulli(1/2) and $\eta$ is the effect
of a uniformly chosen one of the two alleles from a uniformly chosen parent
at a uniformly chosen locus.
% $\eta_\ell^{[i]}$ is the effect of the allele in parent $i$ at locus $\ell$,
Since $|X-1/2| = 1/2$, we'd therefore like to know
if $\P\{|\eta|>2t\}$ is proportional to $t^{-\alpha}$,
i.e., the value of
$$
    \lim_{t \to \infty} \frac{ - \log \P\{ |\eta| > 2 t \} }{ \log t } = \alpha ,
$$
if the limit exists.
Let $p_\ell$ be the minor allele frequency at the $\ell^\text{th}$ locus;
since the data we have assigns effect 0 to the major allele,
$\eta_\ell = 0$ with probability $1-p_\ell$.
Therefore, if we have estimated effects for $M$ SNPs
with minor allele frequency $p_\ell$ and effect size $e_\ell$ for the minor allele,
for $1 \le \ell \le M$,
then
$$
    \P\{ |\eta_{\ell}| > 2t \} \approx \frac{1}{M} \sum_{\ell : |e_\ell| > 2t} p_\ell .
$$
Note that the relevant effect size distribution here is weighted by frequency,
which is necessary because we're looking at the deviation of a typical offspring from their parents,
and the chance a given allele is carried by a random parent is given by the frequency.
(This weighting will make a difference, as frequencies and effect sizes are often correlated in practice.)
So, to obtain a per-trait estimate of $\alpha$,
we plot $\log \frac{1}{M} \sum_{\ell : |e_\ell| > t} p_\ell$ against $\log t$
for a sequence of values of $t$,
and fit a linear model to the tail.
(To do this,
we take as the ``tail''
all values of $t$ for which the number of SNPs with absolute effect above $t$
is at least 20 and at most 10\% of all SNPs.)
Examples are shown in Figure~\ref{fig:example_snps}.

@@

Under the conditions of the proposition, \llabel{pop_not_gaussian}
the parental traits, $Z^{[1]}_M$ and $Z^{[2]}_M$,
are also (jointly) Gaussian.
(This was not an assumption, however.)
If parents are chosen uniformly, then
the distribution of, say, $Z^{[1]}$ is just the population's trait distribution.
This seems wrong, since it is well-known that forces such as selection or migration
can make the population distribution non-Gaussian.
However, there is no contradiction:
we have stated the proposition only in terms of the \emph{first} generation
of offspring of unrelated parents \citep[as in][]{barton2017infinitesimal}.
Proposition~\ref{prop:parental_contribs} does not imply that
the distribution of traits in the offspring generation is Gaussian:
unless all offspring are unrelated,
it will be a collection of correlated Gaussians,
which is not itself Gaussian.
(As an extreme example, suppose that half the offspring are produced by the two parents
with largest trait values, and the other half by the parents with the smallest trait values;
then although each offspring's distribution about the midparent is Gaussian,
the offspring's population distribution is a mixture of two Gaussians
about these two midparents.)
What about further generations?
A similar statement to the proposition
holds for the offspring of two parents in an arbitrary pedigree,
using the Skitovich-Darmois theorem \citet{kagan1973characterization}
% except that the portion of the genome shared in common by the parents is unconstrained.
-- however, there is nothing to be gained by the additional generality.

Finally, note that we follow \citet{barton2017infinitesimal} by assuming that loci are independent
(\ie no linkage disequilibrium) \revpoint{1}{1}
in the parental generation.
% (They are not necessarily identically distributed, however,
% so the Central Limit Theorem need not apply \emph{a priori}.)
One might then wonder if by relaxing this assumption
one could find a model in which the Mendelian sampling term was independent of midparent value
and yet had a non-Gaussian distribution.
To be interesting, such a model would need to maintain the nonindependence structure
that guarantees these properties,
which seems hard to arrange.

@@

Leaving aside 
% -- as the Gaussian-population approximation frequently does --
the question of whether or not some combination of effect sizes, dominance, and epistasis can justify non-Gaussian, trait-independent,  Mendelian sampling terms, we might reasonably ask when (or if)
deterministic mutation-selection balance is possible in a model with non-Gaussian Mendelian sampling terms
that retains independence of these terms.
(Indeed, above we have put substantial restrictions on what models of inheritance
might lead to such models;
in particular,
we are \emph{not} working with the explicit sum-of-$\eta_\ell$ model of the previous sections.) \revpoint{1}{2}
We might also ask whether such a model
might still reasonably approximate an additive model with non-Gaussian effects,
and for the purpose of investigating this with simulations,
some calculations will be helpful.

To summarize, in this section we will uncritically assume that \llabel{clarification3}
the independence assumption of the infinitesimal model holds,
but with an arbitrary distribution for the Mendelian sampling term,
and ask which population trait distributions are possible.
To do this, we work at a higher level,
ignoring the genetic basis of the trait
\citep[and certainly not using the specific set-up of][]{barton2017infinitesimal}.

Concretely, consider a Moran process where an individual whose trait value is $Z$ dies at rate $\mu(Z)$
and is replaced by the offspring of two randomly chosen individuals,
i.e., a new individual with trait \llabel{offspring_eqn}
\begin{align*}
    \frac{Z^{[1]} +Z^{[2]}}{2} + R ,
\end{align*}
where $Z^{[1]}$ and $Z^{[2]}$ are independent draws from the empirical population distribution
and $R$ is an independent draw from the Mendelian sampling distribution
(independent of $Z^{[1]}$ and $Z^{[2]}$, with distribution to be specified). 
(Note that mutation might enter into $R$, but as the underlying genetic basis is not specified,
we do not attempt to disambiguate the various possible contributions.) \llabel{mutation_note}
Mutation-selection balance demands that \revpoint{2}{2}
the distribution of individuals removed by death
and the distribution of individuals added by birth are equal,
\ie that $(Z^{[1]} +Z^{[2]})/2 + R$ is equal in distribution
to a $\mu$-weighted choice of $Z$.
% In other words, for all bounded and continuous functions $f$,
% \begin{equation} \label{eqn:MSB_condition}
%     \E\left[ f\left(\frac{Z^{[1]} +Z^{[2]}}{2} + R \right) \right] = \frac{\E\left[ f(Z) \mu(Z) \right]}{\E[\mu(Z)]},
% \end{equation}
% where the expectation is with respect to the joint law of the population empirical distribution (the law of $Z$, $Z^{[1]}$ and $Z^{[2]}$), and $R$.
% 
% Since the set of functions $\mathcal{S} = \{e^{i \theta x} : \theta \in \R\}$ is separating (see \eg \S 3.4 in \cite{Ethier+Kurtz1986}), it suffices to show that \eqref{eqn:MSB_condition} holds for $f \in \mathcal{S}$, \ie
If the population is large enough, \llabel{deterministic_point}
we can treat the trait distribution as changing deterministically.
Taking the characteristic function of both these distributions,
deterministic mutation-selection balance is therefore equivalent to
\begin{align} \label{eqn:MSB_CF}
    \frac{\E\left[ e^{i \theta Z}\mu(Z) \right]}{\E[\mu(Z)]}
    =
    \E\left[ e^{i\theta\left(\frac{Z^{[1]} + Z^{[2]}}{2} + R \right)}\right] .
\end{align}
Now, we assumed that $Z^{[1]}$, $Z^{[2]}$, and $R$ are independent, so we can write \eqref{eqn:MSB_CF} as 
\begin{align*}
    \frac{\E\left[ e^{i\theta Z} \mu(Z) \right]}{\E[\mu(Z)]} &= \E\left[ e^{i\theta\left(\frac{Z^{[1]} +Z^{[2]}}{2} + R \right)}\right]\\
	% &= \E\left[ e^{i\frac{\theta}{2} Z^{1}}e^{i\frac{\theta}{2} Z^{2}}e^{\i\theta R}\right]\\
    &= \E\left[e^{i\frac{\theta}{2} Z^{[1]}}\right]\E\left[e^{i\frac{\theta}{2} Z^{[2]}}\right]\E\left[e^{i\theta R}\right]\\
	&= \phi\left(\frac{\theta}{2}\right)^{2} \Phi(\theta),
\end{align*}
where
$ \phi(\theta) = \mathbb{E}\left[e^{i\theta Z^{[1]}}\right] = \mathbb{E}\left[e^{i\theta Z^{[2]}}\right] $
and
$ \Phi(\theta) = \mathbb{E}\left[e^{i\theta R}\right] $
are the characteristic functions of $Z^{[j]}$ and $R$, respectively. 
In what follows, we will explore some non-Gaussian solutions $\phi(\theta)$ to equation \eqref{eqn:MSB_CF}.

@@

First, consider the case without selection, so $\mu$ is a constant
which we may take equal to 1. 
(To remind the reader, our goal is therefore to describe \llabel{clarification1}
what forms the population distribution might take in a neutral model
if we assume only that the Mendelian sampling terms are independent of parental values,
and nothing else about the distribution of these terms or the initial population distribution.) 
Then, our condition on the characteristic function simplifies to
\begin{equation}\label{eq:CF_neutral}
	{\textstyle \phi\left(\frac{\theta}{2}\right)^{2}} \Phi(\theta) %e^{-\frac{\eta^{2}\theta^{2}}{2}} 
	= \phi(\theta) ,
\end{equation}
\ie $\phi(\theta)$ is a fixed point of $F$, where
 \[
	F(\phi)(\theta) = {\textstyle \phi\left(\frac{\theta}{2}\right)^{2}} \Phi(\theta) .
\]
Any fixed point $\phi(\theta)$ must be the limit of an arbitrary function, $\varphi(\theta)$, under repeated applications of $F$,
\ie
\begin{equation}\label{eq:fpeq}
\begin{aligned}
	\phi(\theta) 
    &= \lim_{n \to \infty} F^{(n)}(\varphi)(\theta) \\
    &= \lim_{n \to \infty} \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}}\prod_{k=0}^{n-1}\Phi\left(\frac{\theta}{2^{k}}\right)^{2^{k}} .
\end{aligned}
\end{equation}
% Iterating $F$ $n$ times, we get
% \[
% 	F^{(n)}(\varphi)(\theta) =  {\textstyle \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}}}\prod_{k=0}^{n-1} {\textstyle \Phi\left(\frac{\theta}{2^{k}}\right)^{2^{k}}},
% \]
% so that
% \[
% 	\phi(\theta) = \lim_{n \to \infty} \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}}\prod_{k=0}^{n-1}\Phi\left(\frac{\theta}{2^{k}}\right)^{2^{k}}
% \]
is a fixed point whenever this limit exists,
whereas any fixed point $\phi$ of $F$ satisfies  $\phi(\theta) = \lim_{n \to \infty} F^{(n)}(\varphi)(\theta)$
for some function $\varphi(\theta)$.
As we are interested in identifying those fixed points that are characteristic functions, we henceforth assume, without loss of generality, that $\varphi$ is itself a characteristic function (if $\phi$ exists then we can always take $\varphi = \phi$) and that the limit $\lim_{n \to \infty} F^{(n)}(\varphi)(\theta)$ exists.

@@

Now, as characteristic functions, $\varphi$ and $\Phi$ are continuous and $\varphi(0) = \Phi(0) = 1$, and thus both are non-zero in some neighbourhood of 0. In particular, $\psi(\theta) = \Log{\varphi}(\theta)$ and $\Psi(\theta) = \Log{\Phi(\theta)}$ exist in some neighbourhood of 0 as well\footnote{We use $\Log$ to denote the principal value of the complex logarithm, for which the imaginary part always lies in the interval $(-\pi,\pi]$.}.  From the above, we have
\[
	\Log{F^{(n)}(\varphi)(\theta)} = {\textstyle 2^{n} \psi\left(\frac{\theta}{2^{n}}\right)} 
		+ \sum_{k=0}^{n-1}  {\textstyle 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)}.
\]
We briefly explore what possible limiting values are valid characteristic functions. 
We refer to the first term on the left hand side, $\psi_{n}(\theta) = 2^{n} \psi\left(\frac{\theta}{2^{n}}\right)$,  as the \emph{reproduction term} and the remaining sum, $\Psi_{n}(\theta) = \sum_{k=0}^{n-1} 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)$, as the \emph{noise term}, and only consider the case
when both have well-posed limits independent of the other. \llabel{limit_remark} % We don't need to limit to this caee.
Biologically, \llabel{clarification2}
the ``noise term'' is the contribution to variation in the population
generated by the Mendelian sampling terms (\ie by recombination and mutation),
while the ``reproduction term'' is the contribution from variation in the initial generation.

@@

Moreover,  $\psi_{\infty}(\theta) = i m \theta - \gamma |\theta|$ is continuous at 0, and hence so is $\varphi_{\infty}(\theta) = e^{\psi_{\infty}(\theta)}$.  As we observed above, this implies that $e^{\psi_{\infty}(\theta)}$ is itself a characteristic function.  Thus, $e^{\psi_{\infty}(\theta)}$ must satisfy $|e^{\psi_{\infty}(\theta)}| = e^{\Re \psi_{\infty}(\theta)} \leq 1$, whence $\Re \psi_{\infty}(\theta) \leq 0$ and $\gamma \geq 0$.  In particular, if $\gamma > 0$, then we recognize $e^{\psi_{\infty}(\theta)} = e^{im \theta -\gamma|\theta|}$ as the characteristic function of a Cauchy distribution with median m and median absolute deviation $\gamma$ (\ie the canonical $\alpha$-stable distribution with $\alpha=1$), \llabel{cauchy_note} whereas if $\gamma = 0$, then $e^{\psi_{\infty}(\theta)} = e^{im \theta}$ is the Fourier transform of a Dirac mass at $m$, \ie the characteristic function for a monomorphic population with all individuals having trait value equal to $m$.

@@

The crucial step in the derivation of the infinitesimal model in \cite{barton2017infinitesimal} is to show that, \llabel{crucial_step}
following the arguments in \citet{fisher1918correlation}, knowing an individual's trait value gives vanishingly little information about the contribution of any given locus as $M \to \infty$, which in turn allows one to show that the within-family Mendelian sampling term is independent of the parental traits. Here, we will consider how conditioning an individual's trait value affects the law of a single allelic contribution in the Cauchy setting described above. A similar argument can be made for any $\alpha$-stable distribution, but the lack of explicit probability density functions for generic $\alpha \in (0,2)$ adds complexity to the argument without adding any insight.

@@

In simulation we can easily include realistic recombination (instead of unlinked loci) and selection.
We used SLiM v4 \citep{haller2022slim4}
to simulate a discrete-time approximation to the continuous-time Moran model described above
as follows.
Individuals are diploid, hermaphroditic, and sexual;
the genome is of length $10^8$bp with a uniform recombination rate of $10^{-8}$ crossovers per bp;
mutations occur at a rate of $10^{-9}$ per bp. \llabel{mutation_rate}
Each new mutation is independently assigned an ``effect''
drawn from the ``effect size distribution'' (and will be either Gaussian or Cauchy).
The trait of each individual is determined additively
by summing the effects of all mutations they carry across both chromosomes.
Let $\mu(z)$ be the death rate of an individual with trait $z$,
and let $dt$ be a small constant (we took $dt=0.01$).
In all plots, one time unit is approximately one generation.
Then, at each time step
each individual dies with probability $1 - \exp(-dt \mu(z))$;
if there are $k$ such individuals chosen to die in a given time step,
then we choose $k$ individuals uniformly and without replacement
to produce new offspring;
for each such reproduction event the parent chooses a mate uniformly at random from the population.
This maintains the population at a fixed size, $N$.
(Note that individuals may self and individuals chosen to die may also reproduce,
but in a large population these details should be unimportant.)

>>>>

Since the Mendelian sampling term is a sum of terms of the form
$$
    (X_\ell - 1/2) \eta_\ell^{[1]} + (1/2 - X_\ell) \eta_\ell^{[2]},
$$
the appropriate central limit theorem for the sum is determined by
the tail behavior of $|(X - 1/2) \eta|$,
where $X$ is Bernoulli(1/2) and $\eta$ is the effect
of a uniformly chosen one of the two alleles from a uniformly chosen parent
at a uniformly chosen locus.
% $\eta_\ell^{[i]}$ is the effect of the allele in parent $i$ at locus $\ell$,
Since $|X-1/2| = 1/2$, we'd therefore like to know
if $\P\{|\eta|>2t\}$ is proportional to $t^{-\alpha}$,
i.e., the value of
$$
    \lim_{t \to \infty} \frac{ - \log \P\{ |\eta| > 2 t \} }{ \log t } = \alpha ,
$$
if the limit exists.
Let $p_\ell$ be the minor allele frequency at the $\ell^\text{th}$ locus;
since the data we have assigns effect 0 to the major allele,
$\eta_\ell = 0$ with probability $1-p_\ell$.
Therefore, if we have estimated effects for $M$ SNPs
with minor allele frequency $p_\ell$ and effect size $e_\ell$ for the minor allele,
for $1 \le \ell \le M$,
then
$$
    \P\{ |\eta_{\ell}| > 2t \} \approx \frac{1}{M} \sum_{\ell : |e_\ell| > 2t} p_\ell .
$$
Note that the relevant effect size distribution here is weighted by frequency,
which is necessary because we're looking at the deviation of a typical offspring from their parents,
and the chance a given allele is carried by a random parent is given by the frequency.
(This weighting will make a difference, as frequencies and effect sizes are often correlated in practice.)
So, to obtain a per-trait estimate of $\alpha$,
we plot $\log \frac{1}{M} \sum_{\ell : |e_\ell| > t} p_\ell$ against $\log t$
for a sequence of values of $t$,
and fit a linear model to the tail.
(To do this,
we take as the ``tail''
all values of $t$ for which the number of SNPs with absolute effect above $t$
is at least 20 and at most 10\% of all SNPs.)
Examples are shown in Figure~\ref{fig:example_snps}.

@@

Under the conditions of the proposition,
the parental traits, $Z^{[1]}_M$ and $Z^{[2]}_M$,
are also (jointly) Gaussian.
(This was not an assumption, however.)
If parents are chosen uniformly, then
the distribution of, say, $Z^{[1]}$ is just the population's trait distribution.
This seems wrong, since it is well-known that forces such as selection or migration
can make the population distribution non-Gaussian.
However, there is no contradiction:
we have stated the proposition only in terms of the \emph{first} generation
of offspring of unrelated parents \citep[as in][]{barton2017infinitesimal}.
Proposition~\ref{prop:parental_contribs} does not imply that
the distribution of traits in the offspring generation is Gaussian:
unless all offspring are unrelated,
it will be a collection of correlated Gaussians,
which is not itself Gaussian.
(As an extreme example, suppose that half the offspring are produced by the two parents
with largest trait values, and the other half by the parents with the smallest trait values;
then although each offspring's distribution about the midparent is Gaussian,
the offspring's population distribution is a mixture of two Gaussians
about these two midparents.)
What about further generations?
A similar statement to the proposition
holds for the offspring of two parents in an arbitrary pedigree,
using the Skitovich-Darmois theorem \citep{kagan1973characterization},
except that the distribution of the portion of the genome shared in common by the parents
is not constrained.
However, there is little to be gained by the additional generality.

Finally, note that we follow \citet{barton2017infinitesimal}
by assuming that loci in the founding generation are independent
(\ie no linkage disequilibrium). \revpoint{1}{1}
% (They are not necessarily identically distributed, however,
% so the Central Limit Theorem need not apply \emph{a priori}.)
Of course, following the offspring foward through a pedigree
(as \citet{barton2017infinitesimal} do),
the loci will no longer be independent.
One might then wonder if by relaxing the assumption of independence between loci
one could find a model in which the Mendelian sampling term was independent of midparent value
and yet had a non-Gaussian distribution.
To be interesting, such a model would need to maintain the nonindependence structure
that guarantees these properties,
which seems hard to arrange.

@@

Leaving aside 
% -- as the Gaussian-population approximation frequently does --
the question of whether or not some combination of effect sizes, dominance, and epistasis can justify non-Gaussian, trait-independent,  Mendelian sampling terms, we might reasonably ask when (or if)
deterministic mutation-selection balance is possible in a model with non-Gaussian Mendelian sampling terms
that retains independence of these terms.
(Indeed, above we have put substantial restrictions on what models of inheritance
might lead to such models;
in particular,
we are \emph{not} working with the explicit sum-of-$\eta_\ell$ model of the previous sections.)
We might also ask whether such a model
might still reasonably approximate an additive model with non-Gaussian effects,
and for the purpose of investigating this with simulations,
some calculations will be helpful.

To summarize, in this section we will uncritically assume that
the independence assumption of the infinitesimal model holds,
but with an arbitrary distribution for the Mendelian sampling term,
and ask which population trait distributions are possible.
To do this, we work at a higher level,
ignoring the genetic basis of the trait
\citep[and certainly not using the specific set-up of][]{barton2017infinitesimal}.

Concretely, consider a Moran process where an individual whose trait value is $Z$ dies at rate $\mu(Z)$
and is replaced by the offspring of two randomly chosen individuals,
i.e., a new individual with trait
\begin{align*}
    \frac{Z^{[1]} +Z^{[2]}}{2} + R ,
\end{align*}
where $Z^{[1]}$ and $Z^{[2]}$ are independent draws from the empirical population distribution
and $R$ is an independent draw from the Mendelian sampling distribution
(independent of $Z^{[1]}$ and $Z^{[2]}$, with distribution to be specified). 
(Note that mutation might enter into $R$, but as the underlying genetic basis is not specified,
we do not attempt to disambiguate the various possible contributions.)
Mutation-selection balance demands that
the distribution of individuals removed by death
and the distribution of individuals added by birth are equal,
\ie that $(Z^{[1]} +Z^{[2]})/2 + R$ is equal in distribution
to a $\mu$-weighted choice of $Z$.
% In other words, for all bounded and continuous functions $f$,
% \begin{equation} \label{eqn:MSB_condition}
%     \E\left[ f\left(\frac{Z^{[1]} +Z^{[2]}}{2} + R \right) \right] = \frac{\E\left[ f(Z) \mu(Z) \right]}{\E[\mu(Z)]},
% \end{equation}
% where the expectation is with respect to the joint law of the population empirical distribution (the law of $Z$, $Z^{[1]}$ and $Z^{[2]}$), and $R$.
% 
% Since the set of functions $\mathcal{S} = \{e^{i \theta x} : \theta \in \R\}$ is separating (see \eg \S 3.4 in \cite{Ethier+Kurtz1986}), it suffices to show that \eqref{eqn:MSB_condition} holds for $f \in \mathcal{S}$, \ie
If the population is large enough,
we can treat the trait distribution as changing deterministically.
Taking the characteristic function of both these distributions,
deterministic mutation-selection balance is therefore equivalent to
\begin{align} \label{eqn:MSB_CF}
    \frac{\E\left[ e^{i \theta Z}\mu(Z) \right]}{\E[\mu(Z)]}
    =
    \E\left[ e^{i\theta\left(\frac{Z^{[1]} + Z^{[2]}}{2} + R \right)}\right] .
\end{align}
Now, we assumed that $Z^{[1]}$, $Z^{[2]}$, and $R$ are independent, so we can write \eqref{eqn:MSB_CF} as 
\begin{align*}
    \frac{\E\left[ e^{i\theta Z} \mu(Z) \right]}{\E[\mu(Z)]} &= \E\left[ e^{i\theta\left(\frac{Z^{[1]} +Z^{[2]}}{2} + R \right)}\right]\\
	% &= \E\left[ e^{i\frac{\theta}{2} Z^{1}}e^{i\frac{\theta}{2} Z^{2}}e^{\i\theta R}\right]\\
    &= \E\left[e^{i\frac{\theta}{2} Z^{[1]}}\right]\E\left[e^{i\frac{\theta}{2} Z^{[2]}}\right]\E\left[e^{i\theta R}\right]\\
	&= \phi\left(\frac{\theta}{2}\right)^{2} \Phi(\theta),
\end{align*}
where
$ \phi(\theta) = \mathbb{E}\left[e^{i\theta Z^{[1]}}\right] = \mathbb{E}\left[e^{i\theta Z^{[2]}}\right] $
and
$ \Phi(\theta) = \mathbb{E}\left[e^{i\theta R}\right] $
are the characteristic functions of $Z^{[j]}$ and $R$, respectively. 
In what follows, we will explore some non-Gaussian solutions $\phi(\theta)$ to equation \eqref{eqn:MSB_CF}.

@@

First, consider the case without selection, so $\mu$ is a constant
which we may take equal to 1. 
(To remind the reader, our goal is therefore to describe
what forms the population distribution might take in a neutral model
if we assume only that the Mendelian sampling terms are independent of parental values,
and nothing else about the distribution of these terms or the initial population distribution.) 
Then, our condition on the characteristic function simplifies to
\begin{equation}\label{eq:CF_neutral}
	{\textstyle \phi\left(\frac{\theta}{2}\right)^{2}} \Phi(\theta) %e^{-\frac{\eta^{2}\theta^{2}}{2}} 
	= \phi(\theta) ,
\end{equation}
\ie $\phi(\theta)$ is a fixed point of $F$, where
 \[
	F(\phi)(\theta) = {\textstyle \phi\left(\frac{\theta}{2}\right)^{2}} \Phi(\theta) .
\]
Any fixed point $\phi(\theta)$ must be the limit of an arbitrary function, $\varphi(\theta)$, under repeated applications of $F$,
\ie
\begin{equation}\label{eq:fpeq}
\begin{aligned}
	\phi(\theta) 
    &= \lim_{n \to \infty} F^{(n)}(\varphi)(\theta) \\
    &= \lim_{n \to \infty} \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}}\prod_{k=0}^{n-1}\Phi\left(\frac{\theta}{2^{k}}\right)^{2^{k}} .
\end{aligned}
\end{equation}
% Iterating $F$ $n$ times, we get
% \[
% 	F^{(n)}(\varphi)(\theta) =  {\textstyle \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}}}\prod_{k=0}^{n-1} {\textstyle \Phi\left(\frac{\theta}{2^{k}}\right)^{2^{k}}},
% \]
% so that
% \[
% 	\phi(\theta) = \lim_{n \to \infty} \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}}\prod_{k=0}^{n-1}\Phi\left(\frac{\theta}{2^{k}}\right)^{2^{k}}
% \]
is a fixed point whenever this limit exists,
whereas any fixed point $\phi$ of $F$ satisfies  $\phi(\theta) = \lim_{n \to \infty} F^{(n)}(\varphi)(\theta)$
for some function $\varphi(\theta)$.
As we are interested in identifying those fixed points that are characteristic functions, we henceforth assume, without loss of generality, that $\varphi$ is itself a characteristic function (if $\phi$ exists then we can always take $\varphi = \phi$) and that the limit $\lim_{n \to \infty} F^{(n)}(\varphi)(\theta)$ exists.

@@

Now, as characteristic functions, $\varphi$ and $\Phi$ are continuous and $\varphi(0) = \Phi(0) = 1$, and thus both are non-zero in some neighbourhood of 0. In particular, $\psi(\theta) = \Log{\varphi}(\theta)$ and $\Psi(\theta) = \Log{\Phi(\theta)}$ exist in some neighbourhood of 0 as well\footnote{We use $\Log$ to denote the principal value of the complex logarithm, for which the imaginary part always lies in the interval $(-\pi,\pi]$.}.  From the above, we have
\[
	\Log{F^{(n)}(\varphi)(\theta)} = {\textstyle 2^{n} \psi\left(\frac{\theta}{2^{n}}\right)} 
		+ \sum_{k=0}^{n-1}  {\textstyle 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)}.
\]
We briefly explore what possible limiting values are valid characteristic functions. 
We refer to the first term on the left hand side, $\psi_{n}(\theta) = 2^{n} \psi\left(\frac{\theta}{2^{n}}\right)$,  as the \emph{reproduction term} and the remaining sum, $\Psi_{n}(\theta) = \sum_{k=0}^{n-1} 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)$, as the \emph{noise term}, and only consider the case
when both have well-posed limits independent of the other.
Biologically,
the ``noise term'' is the contribution to variation in the population
generated by the Mendelian sampling terms (\ie by recombination and mutation),
while the ``reproduction term'' is the contribution from variation in the initial generation.

@@

Moreover,  $\psi_{\infty}(\theta) = i m \theta - \gamma |\theta|$ is continuous at 0, and hence so is $\varphi_{\infty}(\theta) = e^{\psi_{\infty}(\theta)}$.  As we observed above, this implies that $e^{\psi_{\infty}(\theta)}$ is itself a characteristic function.  Thus, $e^{\psi_{\infty}(\theta)}$ must satisfy $|e^{\psi_{\infty}(\theta)}| = e^{\Re \psi_{\infty}(\theta)} \leq 1$, whence $\Re \psi_{\infty}(\theta) \leq 0$ and $\gamma \geq 0$.  In particular, if $\gamma > 0$, then we recognize $e^{\psi_{\infty}(\theta)} = e^{im \theta -\gamma|\theta|}$ as the characteristic function of a Cauchy distribution with median m and median absolute deviation $\gamma$ (\ie the canonical $\alpha$-stable distribution with $\alpha=1$), whereas if $\gamma = 0$, then $e^{\psi_{\infty}(\theta)} = e^{im \theta}$ is the Fourier transform of a Dirac mass at $m$, \ie the characteristic function for a monomorphic population with all individuals having trait value equal to $m$.

@@

The crucial step in the derivation of the infinitesimal model in \cite{barton2017infinitesimal} is to show that,
following the arguments in \citet{fisher1918correlation}, knowing an individual's trait value gives vanishingly little information about the contribution of any given locus as $M \to \infty$, which in turn allows one to show that the within-family Mendelian sampling term is independent of the parental traits. Here, we will consider how conditioning an individual's trait value affects the law of a single allelic contribution in the Cauchy setting described above. A similar argument can be made for any $\alpha$-stable distribution, but the lack of explicit probability density functions for generic $\alpha \in (0,2)$ adds complexity to the argument without adding any insight.

@@

In simulation we can easily include realistic recombination (instead of unlinked loci) and selection.
We used SLiM v4 \citep{haller2022slim4}
to simulate a discrete-time approximation to the continuous-time Moran model described above
as follows.
Individuals are diploid, hermaphroditic, and sexual;
the genome is of length $10^8$bp with a uniform recombination rate of $10^{-8}$ crossovers per bp;
mutations occur at a rate of $10^{-9}$ per bp.
Each new mutation is independently assigned an ``effect''
drawn from the ``effect size distribution'' (and will be either Gaussian or Cauchy).
The trait of each individual is determined additively
by summing the effects of all mutations they carry across both chromosomes.
Let $\mu(z)$ be the death rate of an individual with trait $z$,
and let $dt$ be a small constant (we took $dt=0.01$).
In all plots, one time unit is approximately one generation.
Then, at each time step
each individual dies with probability $1 - \exp(-dt \mu(z))$;
if there are $k$ such individuals chosen to die in a given time step,
then we choose $k$ individuals uniformly and without replacement
to produce new offspring;
for each such reproduction event the parent chooses a mate uniformly at random from the population.
This maintains the population at a fixed size, $N$.
(Note that individuals may self and individuals chosen to die may also reproduce,
but in a large population these details should be unimportant.)
